\documentclass{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}
\usepackage{tikz}
\title{The Locust}
\author{Mackenzie Norman}
\begin{document}
\maketitle
\textit{}
\section*{Prior Reading}
\begin{list} {}
\item\textit{The Day of The Locust}. 

\item\textit{\href{https://en.wikipedia.org/wiki/Locust}{Wikipedia on Locusts}}. 
\item\textit{The Wretched of The Earth}. 
\end{list}
\section*{Concept}
The locust is a story of three characters, Daniel Paul, Eula, and K. intertwined, experiencing the world.\footnote{You the narrator are the locust. Agitating the characters in the resource starved world.} Begins with K. at home. K. is down to his last beer and the gas station is already closed. Intro to context switching through train of thought\footnote{From Sand Dancer, I don't like the `brooding system'. I'd like for mine to be way more train of thought. - some character and time switching will happen here. perhaps Faulkners original idea for benjys chapter would help clarify things.} Daniel Paul is neurotic and recently getting out of being institutionalized, His thoughts are strewn with footnotes. Eula is plump and radiant. An Abel to K.s Cain. 

The entire story takes place over one night. 



I want to inspect themes of destruction (The Day of the locust is arguably negative towards this ) but I think a cloud of locusts would be beautiful. Also the idea of most of the world being colonized by the rich. Perhaps only a violent destruction can save us.

\section*{Beats}
\subsection*{Intro}
\subsection*{Dancing}
\textit{``Another aspect of the colonized affectivity can be seen when it is drained of energy by the energy of dance\dots The colonized's way of relaxing is precisely this muscular orgy during which the brutal aggressiveness and impulsive violence are channeled.''} 
\paragraph{}

\subsection*{The streets}
\textit{``The colonist's sector is a sector built to last, all stone and steel. It's a sector of lights and paved roads, where the trash cans constantly overflow with strange and wonderful garbage, undreamed-of leftovers.''}
\paragraph{}
As K. and Eula leave the nightclub they meet Daniel. They walk together through the streets. Inspecting the wonderful garbage until 

\subsection{}













\end{document}