\documentclass{article}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\urlstyle{same}
\title{Concept Document - Escape From the cheerful tortoise}
\author{Mackenzie Norman}
\begin{document}
\maketitle
\textit{Note: }This is intended to be far more game than narrative, and ideally would be played in a group. It is also intended to be a drinking game, perhaps with rules added to the bottom of the how to play if \href{https://pr-if.org/doc/play-if-card/play-if-card.pdf}{card}, but obviously it should be fun to play without booze as well. 

\textit{Second Note: } I don't plan on wading into any of the political stuff around the cheerful tortoise. I just thought it was a good place because its such a shit bar. The name might change.

You wake up in what appears to be an empty bar, with no recollection of how you got there and a pounding headache. The bar initially is relatively sparse with a pretty clearly highlighted exit that is locked.( The front door )

\subsection*{Some initial puzzles/quests}
\begin{itemize} 
    \item  Find Tom Moores parking pass
    \item Free Draug so he can return to his wife Sarahodelo.
\end{itemize}

\paragraph{}
Maybe draug and the ghost of Tom Moore are followers?
As you progress ( and your hangover fades ) there is a clear evil overlord. The karaoke system. You set out on a journey to ensure the karaoke system is destroyed for good and dollar beer night is returned. 

\subsection*{Main Puzzles:}
\begin{itemize}
    \item Some electronic circuit that you break or fix with draugs help

    \item Go on the roof thanks to tom moore. 

    \item Collecting shuffleboard pucks(?) and play shuffle board to get the magic number

\end{itemize}

Once the power and the vents are turned off, you simply have to set the karaoke volume to the same number as the current shuffle board score.

Then charlie - the caged eagle - will come out and you have to slay him in laundry based combat. 

\subsection*{Fun Mechanics}
\begin{itemize}
\item you can always find booze and if you drink it you might get some hints 
\item the karaoke machine will randomly mock you
\item 
\end{itemize}




\end{document}